Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-29 paper.tex
Added responses to already completed items

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    Item 6\\
    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
    No response yet.
}\\

@@

10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
{\color{OliveGreen} 
    Item 29\\
    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
    No response yet.
}\\

@@

13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
{\color{OliveGreen}
    Item 32\\
    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
    No response yet.
}\\

>>>>

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    Item 6\\
    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
    Graphs redrawn with a wider range of shading to help identify traces.
}\\

@@

10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
{\color{OliveGreen} 
    Item 29\\
    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
    Changed mention of inductive stirrer to magnetic stirrer.
}\\

@@

13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
{\color{OliveGreen}
    Item 32\\
    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
    Changed references to the CPE model element in the conclusion to the electrical double layer.
}\\
